Using pressure-driven flow systems to evaluate laser speckle contrast imaging

### 2022-09-12 cover_letter.tex
Update cover_letter.tex

This work is significant because it demonstrates the importance of selecting a reliable flow control system when conducting microfluidic characterization studies. The use of syringe pumps introduces additional uncertainty to the resulting measurements that could mask the true sensitivity of an LSCI instrument. Our results suggest that pressure-regulated flow systems should be used instead of syringe pumps when assessing the performance of flow measurement techniques. While we only evaluated LSCI/MESI, these findings are likely relevant for the broader dynamic light scattering community.

>>>>

This work is significant because it demonstrates the importance of selecting a reliable flow control system when characterizing optical techniques such as laser speckle imaging or laser Doppler. The use of syringe pumps introduces additional uncertainty to the resulting measurements that could mask the true sensitivity of an LSCI instrument. Our results suggest that pressure-regulated flow systems should be used instead of syringe pumps when assessing the performance of flow measurement techniques. While we only evaluated LSCI/MESI, these findings are likely relevant for the broader dynamic light scattering community.
